Significant declines in standardised test scores due to COVID-19 school closures disproportionately affect vulnerable students: A replication analysis using data from the United States and a case study on the Netherlands

### 2024-02-14 paper/paper.qmd
Updated introduction

In studying the scope of school closures across the United States (US), they reported that the country experienced, on average, one of the highest number of days of school closed between January 2020 to December 2021 worldwide [@Jack_Oster_2023]. Jack and Oster [-@Jack_Oster_2023] also found that the duration of school closures varies with local demographic characteristics, with more disadvantaged districts facing more prolonged closures. The study population was grade 3 to 8 students across 21 major American states, being Arkansas (AR), Colorado (CO), Connecticut (CT), Georgia (GA), Idaho (ID), Kansas (KS), Louisiana (LA), Massachusetts (MA), Minnesota (MN), Mississippi (MS), Missouri (MO), New Hampshire (NH), Ohio (OH), Pennsylvania (PA), Rhode Island (RI), South Carolina (SC), South Dakota (SD), Virginia (VA), Wisconsin (WI), West Virginia (WV) and Wyoming (WY). The estimand was the impact of COVID-19 closures on academic performance. They found considerable declines in test scores during the 2020-2021 academic year, with declines larger in school districts with less in-person instruction [@Jack_Oster_2023]. On average, pass rates fell from 2019 to 2021 by an average of 12.8 percentage points in mathematics and 6.8 in English Language Arts (ELA) [@Jack_Oster_2023].

@@

This dataset is a `.csv` version of `scores_lm_demographics.dta`, obtained from the replication package of “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@Jack_Oster_2], published in the American Economic Association’s *AER: Insights* [@citeAEA]. Data are obtained from the Departments of Education of the aforementioned 21 US states, each of whom collect data from constituent schools, school boards and school authorities [@DeptsEd]. The dataset contains extensive information on school districts across these 21 states, including shares of students by race, shares of schooling done in-person, and changes in average test scores in both Mathematics and ELA from the previous year across the years 2018-2019 and 2021-2022. Note no information on test scores are available for 2020, as all standardised assessments were cancelled due to the pandemic.

>>>>

In studying the scope of school closures across the United States (US), they reported that the country experienced, on average, one of the highest number of days of school closed between January 2020 to December 2021 worldwide [@Jack_Oster_2023]. Jack and Oster [-@Jack_Oster_2023] also found that the duration of school closures varies with local demographic characteristics, with more disadvantaged districts facing more prolonged closures.They found considerable declines in test scores during the 2020-2021 academic year, with declines larger in school districts with less in-person instruction. On average, pass rates fell from 2019 to 2021 by an average of 12.8 percentage points in mathematics and 6.8 in English Language Arts (ELA) [@Jack_Oster_2023].

@@

This dataset is a `.csv` version of `scores_lm_demographics.dta`, obtained from the replication package of “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@Jack_Oster_2], published in the American Economic Association’s *AER: Insights* [@citeAEA]. Data are obtained from the Departments of Education for the 21 major American states, being Arkansas (AR), Colorado (CO), Connecticut (CT), Georgia (GA), Idaho (ID), Kansas (KS), Louisiana (LA), Massachusetts (MA), Minnesota (MN), Mississippi (MS), Missouri (MO), New Hampshire (NH), Ohio (OH), Pennsylvania (PA), Rhode Island (RI), South Carolina (SC), South Dakota (SD), Virginia (VA), Wisconsin (WI), West Virginia (WV) and Wyoming (WY). Each state collects data from constituent schools, school boards and school authorities [@DeptsEd]. The dataset contains extensive information on school districts across these 21 states, including shares of students by race, shares of schooling done in-person, and changes in average test scores in both Mathematics and ELA from the previous year across the years 2018-2019 and 2021-2022. Note no information on test scores are available for 2020, as all standardised assessments were cancelled due to the pandemic.
